---
title: "Reproducible Research: Peer Assessment 1"
author: "Omyung Richard Kwon"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data
1. Load the data  
2. Process/transform the data (if necessary) into a format suitable for your analysis
  
```{r loadfile}
setwd("C:\\Users\\kwonr\\Projects\\ReproducibleResearch\\RepData_PeerAssessment1")
activity<-read.csv("activity.csv", header=TRUE)
activity$date <- as.Date(activity$date, "%Y-%m-%d")
str(activity)
```


## What is mean total number of steps taken per day?

1. Calculate the total number of steps taken per day
2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day
3. Calculate and report the mean and median of the total number of steps taken per day
  
```{r}
library(ggplot2)
sumbydate <- aggregate(x=activity$steps, by=list(activity$date), FUN=sum, na.rm=TRUE)
names(sumbydate) <- c("date", "totalsteps")

q <- ggplot (sumbydate, aes(x=totalsteps)) + geom_histogram(binwidth=500)
q <- q + labs(title="Daily Steps", x="Total Steps", y = "Frequency")
print(q)

mean(sumbydate$totalsteps)
median(sumbydate$totalsteps)
```
  


## What is the average daily activity pattern?


1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


```{r}
intv.avg <- aggregate(activity$steps, by=list(activity$interval), FUN=mean, na.rm=TRUE)
names(intv.avg) <- c("interval", "avgsteps")

q <- ggplot(intv.avg, aes(x=interval, y=avgsteps))
q <- q + geom_line(color="red")
q <- q + labs(title="Average Daily Steps by Interval", x="Intervals", y="Avg. Steps")
print(q)

intv.avg[intv.avg$avgsteps == max(intv.avg$avgsteps), ]
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
